Examining background gene lists in clusterProfiler - RNA-seq example

### 2024-06-05 analysis/analyse_rnaseq1.Rmd
fig size

---
title: "Examining background gene lists in clusterProfiler - RNA-seq example"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
theme: cosmo
---

>>>>

---
title: "Examining background gene lists in clusterProfiler - RNA-seq example"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 7
theme: cosmo
---
